Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-11 draft/accordionComplexSurfaces.tex
missing crossref
illustration last thm

We conclude this section with four families of examples.

@@

\begin{example}
\label{exm:gcdVectorsWalks}
For instance, the $\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of the facet illustrated in \fref{} are given by
\[
\gvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	-1\!\! & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\cvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & \!\!-1 & \!\!\!\circled{1} \\
	0 & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\dvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	0 & 0 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\]
(\ie columns are the $\b{g}$-, $\b{c}$-, $\b{d}$-vectors of the elements of the facet).

@@

\begin{theorem}
Let~$\bar Q$ be a locally gentle bound quiver such that~$\NKC$ is finite. The collection of cones
\[
\gvectorFan \eqdef \bigset{\R_{\ge0} \gvectors{F}}{F \text{ non-kissing face of } \RNKC}.
\]
is a complete simplicial fan, called the \defn{$\b{g}$-vector fan} of~$\bar Q$.
Moreover, $\gvectorFan$ is the normal fan of the \defn{$\bar Q$-associahedron} defined equivalently as
\begin{itemize}
\item the convex hull of the points~$\point{F} \eqdef \sum_{\omega \in F} \KN(\omega) \, \cvector{\omega}{F}$ for all facets~${F \in \RNKC}$,~or
\item the intersection of the halfspaces~$\HS{\omega} \eqdef \bigset{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$ for all walks~$\omega$ on~$\bar Q$,
\end{itemize}
where $\KN(\omega) \eqdef \sum_{\omega'} \KN(\omega,\omega')$ is the (finite) sum of the kissing numbers of Definition~\ref{def:kissingNumber}.
\end{theorem}

@@

\vincent{Should we add an example? One of the pictures of~\cite{PaluPilaudPlamondon}?}

>>>>

We conclude this section with four families of examples that illustrate the computation of~$\surface_{\bar Q}$.

@@

\begin{example}
\label{exm:gcdVectorsWalks}
For instance, the $\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of the facet illustrated in \fref{fig:gcdVectors} are given by
\[
\gvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	-1\!\! & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\cvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & \!\!-1 & \!\!\!\circled{1} \\
	0 & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\dvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	0 & 0 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\]
(\ie columns are the $\b{g}$-, $\b{c}$-, $\b{d}$-vectors of the elements of the facet).

@@

\begin{theorem}
\label{thm:fanAssociahedron}
Let~$\bar Q$ be a locally gentle bound quiver such that~$\NKC$ is finite. The collection of cones
\[
\gvectorFan \eqdef \bigset{\R_{\ge0} \gvectors{F}}{F \text{ non-kissing face of } \RNKC}.
\]
is a complete simplicial fan, called the \defn{$\b{g}$-vector fan} of~$\bar Q$.
Moreover, $\gvectorFan$ is the normal fan of the \defn{$\bar Q$-associahedron} defined equivalently as
\begin{itemize}
\item the convex hull of the points~$\point{F} \eqdef \sum_{\omega \in F} \KN(\omega) \, \cvector{\omega}{F}$ for all facets~${F \in \RNKC}$,~or
\item the intersection of the halfspaces~$\HS{\omega} \eqdef \bigset{\b{x} \in \R^{Q_0}}{\dotprod{\gvector{\omega}}{\b{x}} \le \KN(\omega)}$ for all walks~$\omega$ on~$\bar Q$,
\end{itemize}
where $\KN(\omega) \eqdef \sum_{\omega'} \KN(\omega,\omega')$ is the (finite) sum of the kissing numbers of Definition~\ref{def:kissingNumber}.
\end{theorem}

@@

We have borrowed \fref{fig:fanAssociahedron} from~\cite{PaluPilaudPlamondon} to illustrate Theorem~\ref{thm:fanAssociahedron}.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.5]{fanAssociahedron1}}
	\centerline{\includegraphics[scale=.5]{fanAssociahedron2}}
	\caption{The $\b{g}$-vector fan~$\gvectorFan$ (left) and the $\bar Q$-associahedron~$\Asso$ (right) of two gentle quivers. Illustration borrowed from~\cite{PaluPilaudPlamondon}.}
	\label{fig:fanAssociahedron}
\end{figure}
